Automatic Matching of Bullet Lands

### 2016-01-20 imaging-paper.Rnw
last massaging

Counting the maximal number of CMS is part of current practice to identify bullet matches~\citep{nichols:1997, nichols:2003, nichols:2003b}. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. 
\hh{ Note that the definition of CMS given in this paper does not match the one given in \citet{thompson:2013}. There, CMS is defined only in terms of matching peaks without regarding valleys. Additionally, peaks in  \citet{thompson:2013} are  used only if they can be identified and matched `within a tolerable range' between lands. The definition given here is computationally less complex, but should yield highly correlated values, because of the requirement to only consider signatures from a stable region in the land (see Section~\ref{sec:heights} for further details on stability of regions). In the Hamby study, the definition of CMS by \citet{thompson:2013} leads to approximately half of the values of CMS defined in this paper (with a correlation coefficient between the values of the two definitions of about 0.92). }
For lead bullets, such as used in the Hamby study, \citet{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. \hh{Biasotti's four or more consecutive lines translates to eight or more with our definition. } %We will assess the claim that eight or more consecutive lines are sufficient for a match in the next section.

@@

\begin{figure}[hbtp]
  \centering
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='.65\\textwidth'>>=
library(rpart)
library(rpart.plot)
library(RColorBrewer)
vals = alpha(brewer.pal(3, name="Paired"), alpha=0.5)
names(bstats)[9:10] <- c("#matches", "#non-matches")
includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km"))
cc <- read.csv("csvs/crosscuts-25-new.csv")
# cc$bullet <- gsub(".*//","",cc$path)
# cc$bullet <- gsub(".x3p", "", cc$bullet)
# bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
#                   bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

@@

\section*{Acknowledgment} 
%Thanks to David Baldwin for pointing us to the NIST database and introducing us to the basic terms.
Thanks to the men and women behind the software R~\citep{R}, and the authors of the R packages  knitr~\citep{knitr} and ggplot2~\citep{ggplot2}.

>>>>

Counting the maximal number of CMS is part of current practice to identify bullet matches~\citep{nichols:1997, nichols:2003, nichols:2003b}. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. 
 Note that the definition of CMS given in this paper does not match the one given in \citet{thompson:2013}. There, CMS is defined only in terms of matching peaks without regarding valleys. Additionally, peaks in  \citet{thompson:2013} are  used only if they can be identified and matched `within a tolerable range' between lands. The definition given here is computationally less complex, but should yield highly correlated values, because of the requirement to only consider signatures from a stable region in the land (see Section~\ref{sec:heights} for further details on stability of regions). In the Hamby study, the definition of CMS by \citet{thompson:2013} leads to approximately half of the values of CMS defined in this paper (with a correlation coefficient between the values of the two definitions of about 0.92). 
For lead bullets, such as used in the Hamby study, \citet{biasotti:1959} considered four or more consecutive peaks (corresponding to eight or more consecutive lines in our definition) to be sufficient evidence of a match.  %We will assess the claim that eight or more consecutive lines are sufficient for a match in the next section.

@@

\begin{figure}[hbtp]
  \centering
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='.7\\textwidth'>>=
library(rpart)
library(rpart.plot)
library(RColorBrewer)
vals = alpha(brewer.pal(3, name="Paired"), alpha=0.5)
names(bstats)[9:10] <- c("#matches", "#non-matches")
includesVar <- setdiff(names(bstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km"))
cc <- read.csv("csvs/crosscuts-25-new.csv")
# cc$bullet <- gsub(".*//","",cc$path)
# cc$bullet <- gsub(".x3p", "", cc$bullet)
# bstats$flagged <- bstats$b2 %in% cc$bullet[which(is.na(cc$cc))] |
#                   bstats$b1 %in% cc$bullet[which(is.na(cc$cc))]

@@

\section*{Acknowledgment} 
Thanks to David Baldwin for pointing us to the NIST database and doing a Ballistics 101 for us.
Thanks to the men and women behind the software R~\citep{R}, and the authors of the R packages  knitr~\citep{knitr} and ggplot2~\citep{ggplot2}.
